Retrofitting Effect Handlers onto OCaml

### 2021-03-25 retro-concurrency.tex
tweak
typo and add acks

The need to host millions of continuations at the same time rules out the use
of a large contiguous stack space as in C for continuations. Instead, we resort
to using small initial stacks and growing the stacks on demand. As a result,
OCaml functions, irrespective of whether they use effect handlers, need to
perform stack overflow checks, and external C functions (which do not have stack
overflow checks) must be performed on a separate system stack. Additionally, we
must generate DWARF stack unwind tables for stacks that may be non-contiguous.
In this work, we develop the compiler and runtime support for implementing
efficient effect handlers for OCaml that satisfy these requirements.

@@

Multicore OCaml supports backtraces for continuations in addition to backtraces
of the current stack as in stock OCaml. Using effect handlers in a system such
as a web server aides debugging and profiling because it is possible to get a
backtrace snapshot of all current requests. Such a feature is available in
Go~\cite{gopprof}, but not in OCaml concurrency libraries such as Async and
Lwt which lack the notion of a thread.

@@

We thank the PLDI reviewers and our shepherd, Matthew Flatt, whose comments
substantially improved the presentation. This research was funded via a Royal
Commission for the Exhibition of 1851 and Darwin College Research Fellowships,
and by grants from Jane Street and Tezos Foundation.

>>>>

The need to host millions of continuations at the same time rules out the use
of a large contiguous stack space as in C for continuations. Instead, we resort
to using small initial stacks and growing the stacks on demand. As a result,
OCaml functions, irrespective of whether they use effect handlers, need to
perform stack overflow checks, and external C functions (which do not have stack
overflow checks) must be performed on a separate system stack. Additionally, we
must generate DWARF stack unwind tables for stacks that may be non-contiguous.
In this work, we develop the compiler and runtime support required for implementing
efficient effect handlers for OCaml that satisfy these requirements.

@@

Multicore OCaml supports backtraces for continuations in addition to backtraces
of the current stack as in stock OCaml. Using effect handlers in a system such
as a web server aids debugging and profiling because it is possible to get a
backtrace snapshot of all current requests. This feature is available in
Go~\cite{gopprof}, but not in OCaml concurrency libraries such as Async and
Lwt which lack the notion of a thread.

@@

We thank Sam Lindley, Franc\'{o}is Pottier, the PLDI reviewers and our shepherd, Matthew Flatt, whose comments substantially improved the presentation. This research was funded via Royal Commission for the Exhibition of 1851 and Darwin College Research Fellowships,
and by grants from Jane Street and the Tezos Foundation.
